### 2015-02-28 paper_40_cri.tex
file rename to cri

\section{MASTER PERFORMANCE INDICATOR (MPI)}
\label{sec:MPI}

    Software development organizations struggle to measure overall performance.  
    The Master Performance Indicator (MPI) is an algorithm to provide a single 
    number score to measure the performance of a software development organization. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  MPI is a collection of the following 5 
    elements, which are actually KRIs,
    for a software development organization.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate MPI
    score is calculated for each element and 
    then aggregated together to form an overall 
    MPI score.  A new MPI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    \textbf{MPI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements}.  MPI is made to be easily 
    expandable to other elements if desired.

    The scores for MPI will range from -1, indicating the worst 
    performance, all the way to +1, indicating perfection.
    A score of 0 is an indication of meeting the basic expectations. 
    A negative score indicates under-performance and a 
    positive score indicates over-performance.   Here are some 
    examples. An MPI score of 0.35 means the organization is 
    performing 35\% better than expected.  Conversely, a score 
    of -0.15 means an organization is performing 15\% worse than expected.

    Below are the attributes of the MPI scoring.
    \begin{itemize}
        \item The range of scores must have equal values above and below 0
        \item The minimum score must equate to the worst possible 
            performance, however that is defined
        \item Similarily, the maximum score must equate to the best possible performance.  
        \item A score of 0 must be average (or expected) performance
        \item All individual elements must have the same scoring range
    \end{itemize}

@@

    \subsection{ELEMENTS OF MPI}
        The MPI score consists of data collected from five
        different elements of an SDO.  
        \begin{enumerate}
            \item Quality
            \item Availability
            \item Satisfaction
            \item Schedule
            \item Requirements
        \end{enumerate}
        These five elements will be outline in the next sections.

@@

            \paragraph{QUALITY DATA}
                In order to properly score the quality of an SDO,
                certain data needs to be obtained in order to measure
                performance. Table \ref{tab:qualitydata} identifies
                the columns of data that will be used to create
                a score for the quality element of MPI.  
                Each column is classified as \textit{required} or
                \textit{optional}.  That is to allow some flexibility
                in the model for organizations that collect
                varying amounts of data.

@@

                    \caption{QUALITY DATA NEEDED FOR MPI}
                    \label{tab:qualitydata}
                \end{longtable}

@@

                Once a model has been found, it will be labeled as $f$ and it
                will not change.  The function $f$ can be the same for all 
                Application IDs or it can be different for each Application ID
                or any combination of Application IDs.   It serves as the 
                quality baseline for MPI. 
                All future quality scores will be dependent upon the original
                $f$.  Once set, the model will not change.

@@

        \subsubsection{AVAILABILITY}
            All the new requirements and great quality do not matter if the software is not available.
            All the new features and great quality do not matter if the software is not available.  Thus it
            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, an SLA is a 
            contract specifying the amount of time software will be available during a
            given time period. } and measure 
            performance against that SLA.  The following section will outline to data needed to properly
            calculate an SLA and the data needed to calculate the MPI score for availability.

@@

            \paragraph{AVAILABILITY DATA}
                Table \ref{tab:availdata} identifies the necessary data to calculate
                the MPI element score for availability.  Notice the three optional 
                fields: \textit{Uptime}, \textit{Scheduled Downtime}, and 
                \textit{Unscheduled Downtime}; they are optional because they can be
                used to calculated the \textit{Percent Uptime}.  The \textit{Percent Uptime}
                is the important value for the MPI schedule score.  Here are the two common
                approaches for calculating percent uptime:

@@

                    \caption{AVAILABILITY DATA NEEDED FOR MPI}
                    \label{tab:availdata}
                \end{longtable}

@@

            \textit{If one element of MPI was to be rated as the most important, satisfaction
            would be it.}  
            Without satisfied customers, the rest of the measures do not matter.
            For example, having a quality
            application that is always available does not matter if the
            application is not what the customer wants.

            Surveys are used to measure satisfaction for MPI.  A series of statements will
            be presented to all or a subset of the customers.  Any customer that chooses
            to respond to the survey is considered a respondent.  A respondent can rate
            statements based upon a Likert Scale\footnote{"The Likert Scale presents 
            respondents with a series of (attitude) dimensions, which fall along a
            continuum." \cite{Cowles2015}} with a numerical response where the 
            minimum value indicates maximum
            disagreement and the maximum value indicates
            the maximum agreement. Common rating scales would be
            from 1 to 5 or from 1 to 3.  An example survey can be seen in Table 
            \ref{tab:samplesurvey}.

@@

                \begin{description}
                \item[Text] \hfill \\
                    The specific text used in the questions or statments
                    is very important.  The text cannot be too vague.  Also, the text
                    must be clear enough to eliminate misinterpretation. Survey
                    questions must be complete and not include gaps.  For example, if
                    an age range is presented, it must include all possible ages.  These
                    are just some of the difficulties with getting the text correct
                    in surveys. 
                \item[Number and Ordering] \hfill \\
                    The number of questions is important.  Too many questions and the 
                    respondents will lose interest and begin responding without the
                    adequate attention needed.  Plus, if the survey is too long there
                    is the risk of quitting before completion.  A short survey might
                    not cover the adequate amount of material.  Both short and long
                    surveys run the risk of providing inaccurate responses.  After
                    determining the best number of questions, the ordering of the questions
                    is important.  Previous survey questions can have an unintended 
                    impact on responses.  Thus, the ordering of questions needs to be
                    addressed. 
                \item[Sampling] \hfill \\
                    Next is the issue of sampling.  Not every customer can be surveyed, so 
                    sample sets os customers need to be presented with a survery.  
                    In the case of MPI, there are 2 possible scenarios for sampling.  
                    \begin{description}
                    \item[First]
                    When an SDO is part of a larger organization, there typically is
                    a small number of business partners that help to guide and 
                    direct the work performed by the SDO.  In this case, the business 
                    partners might be the the ones offering survey responses and they 
                    should all be willing to respond.  Thus, those business partners 
                    represent the entire population, and the surveys should result in 
                    a 100\% response rate which is technically a census.  
                    The only bias that will be present here is the bias of the business 
                    partners and sampling cannot control for that.

@@

            \paragraph{SATISFACTION DATA}
                Once the surveys have been distributed and the results collected, Table
                \ref{tab:satisfactiondata} displays the data that needs to be collected 
                in order to calculate the satisfaction element score for MPI.
                \begin{longtable}{@{}l rr rr}
                    \toprule%
                     \centering%
                     {\bfseries Column Name}
                     & {\bfseries Data Type}
                     &  \\

@@

                    \caption{SATISFACTION DATA NEEDED FOR MPI}
                    \label{tab:satisfactiondata}
                \end{longtable}

@@

            The MPI schedule score provides a numeric value to indicate the amount 
            schedules are missed or exceeded.  The score provides a cumulative measure
            of the performance as compared to other months.
            The score is based upon the historical deviance of estimates for
            projects.  Projects completing on time will be given a score of 0.
            Projects finishing early will be rewarded with positive scores increasing toward
            $k$. Alternatively, 
            late projects will be given negative scores that approach $-k$ as the projects
            become more late.

@@

                In order to calculate the schedule score, certain dates
                need to be present. Table \ref{tab:scheduledata} outlines
                the necessary data for schedules.  One date is considered
                optional as it is not used in the MPI calculation, but it
                is an important date that could be useful for future
                enhancements to MPI.

@@

                    \caption{SCHEDULE DATA NEEDED FOR MPI}
                    \label{tab:scheduledata}
                \end{longtable}

@@

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data. There are several techniques for testing the fit
                of a distribution: histograms, chi-square, Kolmogorov-Smirnov, Shapiro-Wilk,
                or Anderson-Darling \cite{Damodaran2015,Kutner2003}.
                The distribution is needed for the Cumulative
                Distribution Function (C.D.F.). The C.D.F. maps the values
                to a percentile rank within the distribution \cite{Downey2011}.
                The C.D.F. will be transformed to create
                the schedule score for MPI. Since all C.D.F. functions fall within the
                range $[0,1]$, the function needs to be shifted to center around 0, and then
                doubled to fill the desired range of $[-1,1]$. Thus the MPI schedule score
                for each project becomes the following.

@@

                    \caption{REQUIREMENTS DATA NEEDED FOR MPI}
                    \label{tab:req}
                \end{longtable}

@@

        \subsubsection{OVERALL MPI SCORE}
            In order to accomplish the single number score that MPI requires,
            the 5 element scores must be combined. The combination of the scores
            is a weighted average.  The weights can be set based upon the 
            priority of the SDO.  Thus, the overall MPI score is calculated as below.

            \[
                MPI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
            \]

    \subsection{CORRELATIONS IN MPI}
        It is possible that 2 or more of the 5 elements of MPI will be correlated.  This means that
        one of the elements can be predicted based upon the values of the other elements.  Although
        it is possible for correlation to occur between any of the elements, the satisfaction element
        is an obvious element which deserves attention due to the human involvement of the surveys. 
        If a schedule is missed or an important requirement dropped, that could have a large negative
        effect on the satisfaction surveys.  The same could be said of quality or availability with regard to 
        the satisfaction.  However, satisfaction is not the only potentially correlated element.  It is also
        possible that a decrease in quality could result in unexpected downtime which could have a
        negative result on availability.  Similarly, if requirements are added, it is possible the schedule
        will be negatively impacted.  Also, if requirements are dropped, the quality might suffer due
        to missing functionality.

        It is impossible to know which or if correlations will always exist.  Thus it is necessary to
        check for correlations after determining element and overall MPI scores.  
        If correlation is determined, the element should not be dropped but rather be weighted less than
        the other elements.  This technique keeps the most data available but lessens the importance of
        the correlated element.

    \subsection{SENSITIVITY OF MPI}
    \label{sub:sensitivity}

        Some simulations will be run with data from each given distribution.  Then the MPI scores
        will be analyzed.
        For more on sensitivity analysis in statistical modeling, see \cite{Saltelli2000}.

    \subsection{MPI COMPARED}

        \subsubsection{MPI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}

            Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus 
            areas  for software
            analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how MPI addresses
            each focus area.  
            As can be seen, MPI clearly addresses the 3 main focus areas of software analytics.  MPI does not provide
            any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
            the focus areas.

            \begin{longtable}{p{3cm}p{11cm}}
                \toprule%
                 \centering%
                 {\bfseries Focus Area}
                 & {\bfseries Why MPI?} \\

@@

                User Experience & One of the 5 elements of MPI is satisfaction.  While not all of the questions focus solely on the user experience, the entire purpose of the survey is to determine if the user is satisfied
                with the software product. Does it have the correct features? Are new features added in a timely manner? Of course, specific survey questions can be created to focus solely on a certain user experience. \\
                \myrowcolour%
                Quality & Again, one of the 5 elements specifically focuses on quality.  MPI provides a single number
                to measure quality.  Therefore, it is easy to track changes in quality over time.  MPI does not address
                how to improve the quality, but without a consistent measurement, it would be impossible to determine the change in quality. \\
                Development Productivity & The combination of MPI elements, schedule and requirements, provide an 
                indication of development productivity. The schedule element measures the productivity
                related to estimated schedule. Similarly, the requirement element measures the amount of
                work actually being completed.  \\

@@

                \caption{SOFTWARE ANALYTICS FOCUS AREAS AND MPI}
                \label{tab:focusareas}
            \end{longtable}

        \subsubsection{MPI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
            and a description of how MPI addresses that specific question.  It is clear
            that MPI addresses the questions.  MPI is a beneficial technique of software
            analytics when applied to software development organizations.

@@

                \toprule%
                 \centering%
                 {\bfseries Question}
                 & {\bfseries Why MPI?} \\

@@

                How much better is my model performing than a naive strategy, such as guessing? & MPI 
                provides consistency which may not exist without it.  Therefore, MPI removes the 
                guesswork of measuring a software development organization. \\
                \myrowcolour%
                How practically significant are the results? & The MPI score is consistent
                and easy to comprehend.  Thus comparison with past performance is quick 
                and simple.  This is a significant advantage for software 
                development organizations. \\
                How sensitive are the results to small changes in one or more of the inputs? & 
                The question was extensively addressed in section \ref{sub:sensitivity}.  It appears MPI is
                not overly sensitive to small changes in the inputs.\\

@@

                \caption{IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND MPI}
                \label{tab:questions}
            \end{longtable}

        \subsubsection{MPI VS. BALANCED SCORECARD}
            Section \ref{sec:bsc} discusses the characteristics of the 
            balanced scorecard.  Table \ref{tab:bsc} presents a
            comparison of the characteristics of a balanced scorecard
            versus MPI.
            As the newer 2 characteristics of a balanced scorecard
            have only existed since 2010 and the adoption is limited,
            the comparison will only be against the original 4 balanced
            scorecard characteristics.

@@

                \toprule%
                 \centering%
                 {\bfseries Balanced Scorecard}
                 & {\bfseries MPI?} 
                 & {\bfseries Explanation} \\

@@

                Financial & No & MPI does not address financial as it is best suited 
                    for an organization that treats software development as a fixed,
                    budgeted expense. If the budget is fixed, MPI provides a number
                    to indicate the amount of value for that fixed budget.  \\
                \myrowcolour%
                Customer Focus & Yes & MPI includes a customer survey which is 
                    completely customer focused.\\
                Internal Process & Yes & MPI is highly focused on internal processes.
                    The MPI elements of schedule and requirement are completely
                    focused on how reality meets the expected process. MPI is
                    negatively impacted when internal processes are followed. \\
                \myrowcolour%
                Learning/Growth & No & MPI does not address this characteristic. \\

@@

                \caption{BALANCED SCORECARD VERSUS MPI}
                \label{tab:bsc}
            \end{longtable}

        \subsubsection{MPI VS. PROJECT MANAGEMENT MEASUREMENT}
            Previously in Section \ref{sec:pm}, the project management
            measurement was presented.   Its greatest limitation is the lack of
            focus on the entire SDO.  Project management measurement says 
            nothing about the availability of the software infrastructure
            or the satisfaction of the users.  It is not near as comprehensive
            as either the balanced scorecard or MPI. Actually, MPI incorporates
            the 5 core measurements from project management.
            Plus, the process productivity
            number is less suitable for upper management and more
            suitable for project teams.  Although it does provide a single
            process productivity number, it is does not have the same focus
            as MPI.

>>>>

\section{CUMULATIVE RESULT INDICATOR (CRI)}
\label{sec:CRI}

    Software development organizations struggle to measure overall performance.  
    The Cumulative Result Indicator (CRI) is an algorithm to provide a single 
    number score to measure the performance of a software development organization. 
    It works by statistically analyzing the past performance of the 
    organization and using that information to score an organization 
    on current performance.  CRI is a collection of the following 5 
    elements, which are actually KRIs,
    for a software development organization.
    \textbf{
    \begin{enumerate}
        \item Quality
        \item Availability
        \item Satisfaction
        \item Schedule
        \item Requirements
    \end{enumerate}
    }
    A separate CRI
    score is calculated for each element and 
    then aggregated together to form an overall 
    CRI score.  A new CRI score will be calculated based
    upon the selection of a given time period (weekly, monthly, quarterly).
    \textbf{CRI is not meant to be comparative between
    organizations, but to measure the amount of increase or decrease
    a single organization exhibits across elements}.  CRI is made to be easily 
    expandable to other elements if desired.

    The scores for CRI will range from -1, indicating the worst 
    performance, all the way to +1, indicating perfection.
    A score of 0 is an indication of meeting the basic expectations. 
    A negative score indicates under-performance and a 
    positive score indicates over-performance.   Here are some 
    examples. An CRI score of 0.35 means the organization is 
    performing 35\% better than expected.  Conversely, a score 
    of -0.15 means an organization is performing 15\% worse than expected.

    Below are the attributes of the CRI scoring.
    \begin{itemize}
        \item The range of scores must have equal values above and below 0
        \item The minimum score must equate to the worst possible 
            performance, however that is defined
        \item Similarily, the maximum score must equate to the best possible performance.  
        \item A score of 0 must be average (or expected) performance
        \item All individual elements must have the same scoring range
    \end{itemize}

@@

    \subsection{ELEMENTS OF CRI}
        The CRI score consists of data collected from five
        different elements of an SDO.  
        \begin{enumerate}
            \item Quality
            \item Availability
            \item Satisfaction
            \item Schedule
            \item Requirements
        \end{enumerate}
        These five elements will be outline in the next sections.

@@

            \paragraph{QUALITY DATA}
                In order to properly score the quality of an SDO,
                certain data needs to be obtained in order to measure
                performance. Table \ref{tab:qualitydata} identifies
                the columns of data that will be used to create
                a score for the quality element of CRI.  
                Each column is classified as \textit{required} or
                \textit{optional}.  That is to allow some flexibility
                in the model for organizations that collect
                varying amounts of data.

@@

                    \caption{QUALITY DATA NEEDED FOR CRI}
                    \label{tab:qualitydata}
                \end{longtable}

@@

                Once a model has been found, it will be labeled as $f$ and it
                will not change.  The function $f$ can be the same for all 
                Application IDs or it can be different for each Application ID
                or any combination of Application IDs.   It serves as the 
                quality baseline for CRI. 
                All future quality scores will be dependent upon the original
                $f$.  Once set, the model will not change.

@@

        \subsubsection{AVAILABILITY}
            All the new requirements and great quality do not matter if the software is not available.
            All the new features and great quality do not matter if the software is not available.  Thus it
            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, an SLA is a 
            contract specifying the amount of time software will be available during a
            given time period. } and measure 
            performance against that SLA.  The following section will outline to data needed to properly
            calculate an SLA and the data needed to calculate the CRI score for availability.

@@

            \paragraph{AVAILABILITY DATA}
                Table \ref{tab:availdata} identifies the necessary data to calculate
                the CRI element score for availability.  Notice the three optional 
                fields: \textit{Uptime}, \textit{Scheduled Downtime}, and 
                \textit{Unscheduled Downtime}; they are optional because they can be
                used to calculated the \textit{Percent Uptime}.  The \textit{Percent Uptime}
                is the important value for the CRI schedule score.  Here are the two common
                approaches for calculating percent uptime:

@@

                    \caption{AVAILABILITY DATA NEEDED FOR CRI}
                    \label{tab:availdata}
                \end{longtable}

@@

            \textit{If one element of CRI was to be rated as the most important, satisfaction
            would be it.}  
            Without satisfied customers, the rest of the measures do not matter.
            For example, having a quality
            application that is always available does not matter if the
            application is not what the customer wants.

            Surveys are used to measure satisfaction for CRI.  A series of statements will
            be presented to all or a subset of the customers.  Any customer that chooses
            to respond to the survey is considered a respondent.  A respondent can rate
            statements based upon a Likert Scale\footnote{"The Likert Scale presents 
            respondents with a series of (attitude) dimensions, which fall along a
            continuum." \cite{Cowles2015}} with a numerical response where the 
            minimum value indicates maximum
            disagreement and the maximum value indicates
            the maximum agreement. Common rating scales would be
            from 1 to 5 or from 1 to 3.  An example survey can be seen in Table 
            \ref{tab:samplesurvey}.

@@

                \begin{description}
                \item[Text] \hfill \\
                    The specific text used in the questions or statments
                    is very important.  The text cannot be too vague.  Also, the text
                    must be clear enough to eliminate misinterpretation. Survey
                    questions must be complete and not include gaps.  For example, if
                    an age range is presented, it must include all possible ages.  These
                    are just some of the difficulties with getting the text correct
                    in surveys. 
                \item[Number and Ordering] \hfill \\
                    The number of questions is important.  Too many questions and the 
                    respondents will lose interest and begin responding without the
                    adequate attention needed.  Plus, if the survey is too long there
                    is the risk of quitting before completion.  A short survey might
                    not cover the adequate amount of material.  Both short and long
                    surveys run the risk of providing inaccurate responses.  After
                    determining the best number of questions, the ordering of the questions
                    is important.  Previous survey questions can have an unintended 
                    impact on responses.  Thus, the ordering of questions needs to be
                    addressed. 
                \item[Sampling] \hfill \\
                    Next is the issue of sampling.  Not every customer can be surveyed, so 
                    sample sets os customers need to be presented with a survery.  
                    In the case of CRI, there are 2 possible scenarios for sampling.  
                    \begin{description}
                    \item[First]
                    When an SDO is part of a larger organization, there typically is
                    a small number of business partners that help to guide and 
                    direct the work performed by the SDO.  In this case, the business 
                    partners might be the the ones offering survey responses and they 
                    should all be willing to respond.  Thus, those business partners 
                    represent the entire population, and the surveys should result in 
                    a 100\% response rate which is technically a census.  
                    The only bias that will be present here is the bias of the business 
                    partners and sampling cannot control for that.

@@

            \paragraph{SATISFACTION DATA}
                Once the surveys have been distributed and the results collected, Table
                \ref{tab:satisfactiondata} displays the data that needs to be collected 
                in order to calculate the satisfaction element score for CRI.
                \begin{longtable}{@{}l rr rr}
                    \toprule%
                     \centering%
                     {\bfseries Column Name}
                     & {\bfseries Data Type}
                     &  \\

@@

                    \caption{SATISFACTION DATA NEEDED FOR CRI}
                    \label{tab:satisfactiondata}
                \end{longtable}

@@

            The CRI schedule score provides a numeric value to indicate the amount 
            schedules are missed or exceeded.  The score provides a cumulative measure
            of the performance as compared to other months.
            The score is based upon the historical deviance of estimates for
            projects.  Projects completing on time will be given a score of 0.
            Projects finishing early will be rewarded with positive scores increasing toward
            $k$. Alternatively, 
            late projects will be given negative scores that approach $-k$ as the projects
            become more late.

@@

                In order to calculate the schedule score, certain dates
                need to be present. Table \ref{tab:scheduledata} outlines
                the necessary data for schedules.  One date is considered
                optional as it is not used in the CRI calculation, but it
                is an important date that could be useful for future
                enhancements to CRI.

@@

                    \caption{SCHEDULE DATA NEEDED FOR CRI}
                    \label{tab:scheduledata}
                \end{longtable}

@@

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data. There are several techniques for testing the fit
                of a distribution: histograms, chi-square, Kolmogorov-Smirnov, Shapiro-Wilk,
                or Anderson-Darling \cite{Damodaran2015,Kutner2003}.
                The distribution is needed for the Cumulative
                Distribution Function (C.D.F.). The C.D.F. maps the values
                to a percentile rank within the distribution \cite{Downey2011}.
                The C.D.F. will be transformed to create
                the schedule score for CRI. Since all C.D.F. functions fall within the
                range $[0,1]$, the function needs to be shifted to center around 0, and then
                doubled to fill the desired range of $[-1,1]$. Thus the CRI schedule score
                for each project becomes the following.

@@

                    \caption{REQUIREMENTS DATA NEEDED FOR CRI}
                    \label{tab:req}
                \end{longtable}

@@

        \subsubsection{OVERALL CRI SCORE}
            In order to accomplish the single number score that CRI requires,
            the 5 element scores must be combined. The combination of the scores
            is a weighted average.  The weights can be set based upon the 
            priority of the SDO.  Thus, the overall CRI score is calculated as below.

            \[
                CRI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
            \]

    \subsection{CORRELATIONS IN CRI}
        It is possible that 2 or more of the 5 elements of CRI will be correlated.  This means that
        one of the elements can be predicted based upon the values of the other elements.  Although
        it is possible for correlation to occur between any of the elements, the satisfaction element
        is an obvious element which deserves attention due to the human involvement of the surveys. 
        If a schedule is missed or an important requirement dropped, that could have a large negative
        effect on the satisfaction surveys.  The same could be said of quality or availability with regard to 
        the satisfaction.  However, satisfaction is not the only potentially correlated element.  It is also
        possible that a decrease in quality could result in unexpected downtime which could have a
        negative result on availability.  Similarly, if requirements are added, it is possible the schedule
        will be negatively impacted.  Also, if requirements are dropped, the quality might suffer due
        to missing functionality.

        It is impossible to know which or if correlations will always exist.  Thus it is necessary to
        check for correlations after determining element and overall CRI scores.  
        If correlation is determined, the element should not be dropped but rather be weighted less than
        the other elements.  This technique keeps the most data available but lessens the importance of
        the correlated element.

    \subsection{SENSITIVITY OF CRI}
    \label{sub:sensitivity}

        Some simulations will be run with data from each given distribution.  Then the CRI scores
        will be analyzed.
        For more on sensitivity analysis in statistical modeling, see \cite{Saltelli2000}.

    \subsection{CRI COMPARED}

        \subsubsection{CRI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}

            Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus 
            areas  for software
            analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how CRI addresses
            each focus area.  
            As can be seen, CRI clearly addresses the 3 main focus areas of software analytics.  CRI does not provide
            any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
            the focus areas.

            \begin{longtable}{p{3cm}p{11cm}}
                \toprule%
                 \centering%
                 {\bfseries Focus Area}
                 & {\bfseries Why CRI?} \\

@@

                User Experience & One of the 5 elements of CRI is satisfaction.  While not all of the questions focus solely on the user experience, the entire purpose of the survey is to determine if the user is satisfied
                with the software product. Does it have the correct features? Are new features added in a timely manner? Of course, specific survey questions can be created to focus solely on a certain user experience. \\
                \myrowcolour%
                Quality & Again, one of the 5 elements specifically focuses on quality.  CRI provides a single number
                to measure quality.  Therefore, it is easy to track changes in quality over time.  CRI does not address
                how to improve the quality, but without a consistent measurement, it would be impossible to determine the change in quality. \\
                Development Productivity & The combination of CRI elements, schedule and requirements, provide an 
                indication of development productivity. The schedule element measures the productivity
                related to estimated schedule. Similarly, the requirement element measures the amount of
                work actually being completed.  \\

@@

                \caption{SOFTWARE ANALYTICS FOCUS AREAS AND CRI}
                \label{tab:focusareas}
            \end{longtable}

        \subsubsection{CRI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
            and a description of how CRI addresses that specific question.  It is clear
            that CRI addresses the questions.  CRI is a beneficial technique of software
            analytics when applied to software development organizations.

@@

                \toprule%
                 \centering%
                 {\bfseries Question}
                 & {\bfseries Why CRI?} \\

@@

                How much better is my model performing than a naive strategy, such as guessing? & CRI 
                provides consistency which may not exist without it.  Therefore, CRI removes the 
                guesswork of measuring a software development organization. \\
                \myrowcolour%
                How practically significant are the results? & The CRI score is consistent
                and easy to comprehend.  Thus comparison with past performance is quick 
                and simple.  This is a significant advantage for software 
                development organizations. \\
                How sensitive are the results to small changes in one or more of the inputs? & 
                The question was extensively addressed in section \ref{sub:sensitivity}.  It appears CRI is
                not overly sensitive to small changes in the inputs.\\

@@

                \caption{IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND CRI}
                \label{tab:questions}
            \end{longtable}

        \subsubsection{CRI VS. BALANCED SCORECARD}
            Section \ref{sec:bsc} discusses the characteristics of the 
            balanced scorecard.  Table \ref{tab:bsc} presents a
            comparison of the characteristics of a balanced scorecard
            versus CRI.
            As the newer 2 characteristics of a balanced scorecard
            have only existed since 2010 and the adoption is limited,
            the comparison will only be against the original 4 balanced
            scorecard characteristics.

@@

                \toprule%
                 \centering%
                 {\bfseries Balanced Scorecard}
                 & {\bfseries CRI?} 
                 & {\bfseries Explanation} \\

@@

                Financial & No & CRI does not address financial as it is best suited 
                    for an organization that treats software development as a fixed,
                    budgeted expense. If the budget is fixed, CRI provides a number
                    to indicate the amount of value for that fixed budget.  \\
                \myrowcolour%
                Customer Focus & Yes & CRI includes a customer survey which is 
                    completely customer focused.\\
                Internal Process & Yes & CRI is highly focused on internal processes.
                    The CRI elements of schedule and requirement are completely
                    focused on how reality meets the expected process. CRI is
                    negatively impacted when internal processes are followed. \\
                \myrowcolour%
                Learning/Growth & No & CRI does not address this characteristic. \\

@@

                \caption{BALANCED SCORECARD VERSUS CRI}
                \label{tab:bsc}
            \end{longtable}

        \subsubsection{CRI VS. PROJECT MANAGEMENT MEASUREMENT}
            Previously in Section \ref{sec:pm}, the project management
            measurement was presented.   Its greatest limitation is the lack of
            focus on the entire SDO.  Project management measurement says 
            nothing about the availability of the software infrastructure
            or the satisfaction of the users.  It is not near as comprehensive
            as either the balanced scorecard or CRI. Actually, CRI incorporates
            the 5 core measurements from project management.
            Plus, the process productivity
            number is less suitable for upper management and more
            suitable for project teams.  Although it does provide a single
            process productivity number, it is does not have the same focus
            as CRI.
